---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# refactor

Refactoring code can be a bit scary, what if we mess something up and end up
with a different output or slower code?

Hopefully no more! {refactor} lets you run both the original and refactored 
version of your code and checks whether the output is the same and if it runs
as fast. Then when you're comfortable with your work you can remove the original version.

## Installation

Install with:

``` r
remotes::install_github("moodymudskipper/refactor")
```

## Examples

```{r}
library(refactor)
```

* `%refactor%`  is used to check that the output value is consistent
* `%refactor2%` also checks that the refactored version runs faster

They'll often be used on the body of a function but can be used on any expression.

Here I intend to correct an inefficient use of the `apply()` function,
but used `pmax` incorrectly:

```{r, error=TRUE}
fun1 <- function(data) {
  apply(data, 1, max)
} %refactor% {
  pmax(data)
}
fun1(cars)
```

Now using it correctly:

```{r}
fun2 <- function(data) {
  apply(data, 1, max)
} %refactor% {
  do.call(pmax, data)
}
fun2(cars)
```

Now let's demonstrate `%refactor2%` by inverting the original and refactored
code, and using bigger data so execution time differences are noticeable :

```{r, error=TRUE}
cars2 <- do.call(rbind, replicate(1000,cars, F))
fun3 <- function(data) {
  do.call(pmax, data)
} %refactor2% {
  apply(data, 1, max)
}
fun3(cars2)

```

## Caveats

We don't control that side effects are the same on both sides, this means
the following for instance might be different in your refactored code 
and you won't be warned about it :

* modified environments
* written files
* printed output
* messages
* warnings
* errors

We might be able to support some of those though.

More importantly since both side are run, side effects will be run twice and in some case
this might change the behavior of the program, so use cautiously.
